Helmet Foam Case Study Report

### 2024-04-29 CS2 Final Draft.qmd
Update CS2 Final Draft.qmd
updated #5

For further and future studies, we recommend that more foam samples are tested, so that there are more observations to work with. The same number of each type of foam should be used, and the treatments such as amplitude and initial stress should be assigned evenly, so each treatment level is fully tested on each type of foam. This will allow for more trustworthy models.

>>>>

For future studies and more reliable models, we recommend testing more foam samples to increase the number of observations that can be used. The same number of each type of foam should be used, and treatments such as amplitude and initial stress should be assigned evenly. This ensures each treatment level is fully tested on each type of foam. We would also recommend regulating the temperature of the testing environment to help provide the best testing conditions.
